Molecular dynamics simulation of synchronization in driven particles

### 2020-12-31 manuscript/manuscript_ajp_2020.tex
updated single particle figure

In Fig.~\ref{fig:0}(b) 
we show the $y-$position of the particle
as a function of time,
where we 
normalize $y$ by the spatial period of the washboard as
$y/\lambda$.
The initial particle position is $y=0$,
where the landscape force is minimum $F^l = 0$.
Subsequent substrate 
%CHECK!!! I THINK THIS IS WRONG!!!
%BY NOT INCLUDING THE SIGN YOU'VE DEFINED IT BACKWARDS!!!!!
%AND LOCATED THE INITIAL POSITION OF THE PARTICLE
%AT A LOCAL MAXIMA!!!!!
%The substrate maxima are located at integer multiples of $y/\lambda = 0, 1, 2 $ 
%and
minima are located at integer multiples $y/\lambda = 1/2, 3/2, 5/2, $ {\it et cetera}.
%This is apparent in the spacing of $y/\lambda$ in time,
%where the visual gaps between positions in Fig.~\ref{fig:0}(b) 
%at half integer multiples $y/\lambda = 1/2, 3/2, 5/2$ indicate regions the particle was moving slowly.
%measure/plot velocity?

@@

%single DC case with figure
%dc_current 0.01
%ac_current 0.2
%ac_frequency 0.0001
%fp_y 0.1
\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{position.png}
\caption{The position as a function of time of a single driven particle
  normalized by the period of the substrate $\lambda$.
  }
\label{fig:0}
\end{figure}
\end{center}

>>>>

In Fig.~\ref{fig:0}(b) 
we show the $y-$position of the particle
as a function of time,
where we 
normalize $y$ by the spatial period of the washboard as
$y/\lambda$.
The initial particle position is $y=0$,
where the landscape force is minimum $F^l = 0$.
Subsequent substrate

@@

%single DC case with figure
%dc_current 0.01
%ac_current 0.2
%ac_frequency 0.0001
%fp_y 0.1
\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{single_particle.pdf}
\caption{(a) The applied driving force $F^D(t)$ where the parameter $F^{DC}$ is ramped to a constant value.  (b) 
  The position as a function of time of a single driven particle
  normalized by the period of the substrate $\lambda$.
  }
\label{fig:0}
\end{figure}
\end{center}
